Asimilación de distintas observaciones

### 2020-11-14 analysis/chapters/experimento_20181122.Rmd
Nuevo E7

```{r Q-diff, fig.cap="Specific humidity difference between experiments in g/Kg", fig.height=3}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "QVAPOR") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
    geom_contour_fill(aes(z = value*1000), breaks = seq(-0.0016, 0.0016, 0.0002)*1000) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-0.0016, 0.0016, 0.0002)*1000,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +

@@

```{r U-diff, fig.cap="Zonal wind difference between experiments in m/s", fig.height=3}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value), reaks = seq(-1.2, 1.2, 0.2)) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-1.2, 1.2, 0.2),
                       labels = round(seq(-1.2, 1.2, 0.2), 1),
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "U difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
   facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r V-diff, fig.cap="Meridial wind difference between experiments in m/s", fig.height=3}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value), reaks = seq(-1.2, 1.2, 0.2)) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-1.2, 1.2, 0.2),
                       labels = round(seq(-1.2, 1.2, 0.2), 1),
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "V difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
   facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

>>>>

```{r Q-diff, fig.cap="Specific humidity difference between experiments in g/Kg", fig.height=3}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "QVAPOR") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E5)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
    geom_contour_fill(aes(z = value*1000), breaks = seq(-0.0016, 0.0016, 0.0002)*1000) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-0.0016, 0.0016, 0.0002)*1000,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +

@@

```{r U-diff, fig.cap="Zonal wind difference between experiments in m/s", fig.height=3}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value), reaks = seq(-1.2, 1.2, 0.2)) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-1.2, 1.2, 0.2),
                       # labels = round(seq(-1.2, 1.2, 0.2), 1),
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "U difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
   facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r V-diff, fig.cap="Meridial wind difference between experiments in m/s", fig.height=3}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value), reaks = seq(-1.2, 1.2, 0.2)) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-1.2, 1.2, 0.2),
                       # labels = round(seq(-1.2, 1.2, 0.2), 1),
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "V difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
   facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

#### FSS for analysis

```{r}
files <- list.files(here("analysis", "data", "derived_data"), 
                    full.names = TRUE,
                    pattern = "fss_3h")

fss <- purrr::map(files, function(f) {

  fread(f) %>% 
    .[, date := as_datetime(date)]
}) %>% 
  rbindlist()

fss %>% 
  ggplot(aes(date, fss)) +
  geom_point(aes(color = exp)) +
  geom_line(aes(color = exp, linetype = factor(w))) +
  facet_grid(w~q)
